---
title: 'Enough is enough: How to sample plant-pollinator networks to make relative comparisons'

author:  

- name: Ignasi Bartomeus
  affilnum: 1
  email: ibartomeus@ebd.csic.es
  
- name: Cristina Botías 
  affilnum: 1 
  
- name: Miguel Ángel Collado 
  affilnum: 1 
  
- name: Óscar Godoy 
  affilnum: 2 
  
- name: Ainhoa Magrach 
  affilnum: '1,3' 

- name: Curro Molina 
  affilnum: 1 
  
- name: Néstor Pérez-Méndez 
  affilnum: 4 
  
- name: Francisco Rodríguez-Sánchez 
  affilnum: 1

affiliation:

- affilnum: 1
  affil: Dept. Ecología Integrativa, Estación Biológica de Donana, Consejo Superior de Investigaciones Científicas, Avda. Américo Vespucio 26, E-41092 Sevilla, Spain
  
- affilnum: 2
  affil: Instituto de Recursos Naturales y Agrobiología, Consejo Superior de Investigaciones Científicas, Avda. Reina Mercedes XX, XXXXX Sevilla, Spain
  
- affilnum: 3
  affil: Euskadi
  
- affilnum: 4
  affil: Argentina
  
output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null
  
  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: no
#bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl

---


```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = FALSE, comment = NA, highlight = TRUE)

## Cache
#opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
#opts_chunk$set(fig.path = "output/figures/")


```


\singlespace

\vspace{2mm}\hrule

Characterising complex networks on interacting species is challenging. Two major stumbling blocks are a) correctly identifying species identity and b) having a sufficient sampling size for detecting all occurring links. A revisión of recently published plant-pollinator networks shows that most published networks group several species into morphospecies or even work at the genus level. In addition, when evaluated, sampling completness is never reached. This has clear implications for describing the network structure, but it is unknown how it affects relative comparisions among networks. Ecologists are often more interested in the relative comparision among communities with contrasting environments or treatments rather than in the absolute values. When two networks are sampled using the same methods, low taxonomic resolution and limited sampling effort may not change its relative comparision, but this has never been tested empirically. I use an intensive sampling of 16 fully resolved plant-pollinator networks acorss an environmental gradient to compare if the relative ranking of the main network propierties changes when increasing taxonomic resolution (from morphospecies tos species) and sampling effort. Then, I tested to which degree recently developed techniques for predicting missing links enhance the relative coparisions of poorly sampled networks. Determining which methods and indexes are robust to relative comparisions is needed in order to empirically test for pressing environmental changes that interacting communities are facing.

\vspace{3mm}\hrule



*Keywords*: networks, pollination, mutualisms, sampling effort

\doublespace

\bleft


# INTRODUCTION





# METHODS







# RESULTS





# DISCUSSION

Discuss.



# CONCLUSIONS



# ACKNOWLEDGEMENTS



# REFERENCES

<div id = "refs"></div>


\eleft

\clearpage


\listoftables


\newpage

```{r Table1, results='asis', echo=FALSE, cache=FALSE}
kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
```


\newpage

```{r Table2, results='asis', echo=FALSE, cache=FALSE}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```


\clearpage

\listoffigures


\newpage

```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

\newpage

\blandscape

```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

\elandscape

\clearpage



```{r sessioninfo, echo = FALSE, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
```

